FLM for growth as function of SPEI

### 2021-03-09 analysis/paper/vital rate models.Rmd
edits based on María's comments

```{r}
s_post_cf <-
  bam(surv ~ 
        s(log_size_prev, bs = "cr") +
        s(plot, bs = "re") + #random intercept
        # s(plot, log_size_prev, bs = "re") + #random slope
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      method = "REML",
      select = TRUE,
      cluster = cl)
```

>>>>

```{r}
s_post_cf <-
  bam(surv ~ 
        s(log_size_prev, bs = "cr") +
        s(plot, bs = "re") + #random intercept
        # s(plot, log_size_prev, bs = "re") + #random slope
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #bimodal response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      method = "REML",
      select = TRUE,
      cluster = cl)
```
